---
title: "w02_d2_tweet_strings"
output: html_notebook
---

```{r}
library(tidyverse)
library(rtweet)
library(janitor)

codeclan_tweets <- read_csv("data/code_clan_tweets.csv")
```
############
3 MVP


Question 1.
Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.

```{r}
glimpse(codeclan_tweets)
view(codeclan_tweets)
```


Question 2.
Find the total number of favourites (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).

```{r}
codeclan_tweets %>% 
  select(is_quote, favorite_count) %>%
  filter(is_quote != "TRUE",) %>% 
  summarise(total_favs =
              sum(favorite_count))
  
```


Question 3.
Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.

```{r}
codeclan_tweets %>% 
  select(source, is_quote, favorite_count) %>%
    filter(is_quote != "TRUE",) %>%
  group_by(source) %>%
  #summarise(total_favs2 =
  #            (sum(favorite_count)/425))
   summarise(mean_favs =
              mean(favorite_count))
```


Question 4.
Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.


```{r}
codeclan_tweets %>%
  select(text, media_type, is_quote, favorite_count) %>%
  mutate(media_type =
           coalesce(media_type, "text")) %>% 
  filter(is_quote != "TRUE",) %>%
  group_by(media_type) %>%
  summarise(total_favs =
              sum(favorite_count)) 

  #  arrange(desc(favorite_count))
  
  
```

Question 5.
Find the mean number of characters that a CodeClan tweet contains. You can either find a way to count the text in the text variable, or use the variable display_text_width which contains a count. Checking both would be a good idea if possible to see if they match (but it’s not essential).

```{r}
codeclan_tweets %>% 
  
  summarise(mean(display_text_width)) 

# it will be different  need to calculate total characters in text column, then divide str_length by the total
```


Question 6.
The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.

```{r}
codeclan_info <- read_csv("data/code_clan_info.csv")
view(codeclan_info)
```

```{r}
codeclan_tweets_status <- left_join(codeclan_tweets, codeclan_info)

codeclan_tweets_status
```


Question 7.
From your new joined data, create a new tibble codeclan_hashtags containing only the tweet_id and convert the hashtags into lowercase for analysis. Keep only those tweets with hashtags.

```{r}
pattern <- "(?i)#[a-z]+"

codeclan_hashtags <- codeclan_tweets_status %>% 
  select(tweet_id, text) %>% 
  mutate(text = tolower(text) %>% 
  filter(text == "#")

  
```


```{r}
codeclan_tweets_status %>% 
  janitor::clean_names()
```


############
4 Extensions


Question 8.
Some tweets have more than one hashtag, denoted by the c( symbols at the start of the string. Use the str_sub() and str_detect() functions and your codeclan_hashtags tibble from above to find all the cases in which the hashtag string begins with charactersc(.
Hint


Question 9.
Use the str_detect() function to find all tweets with text that mentions “Edinburgh”, and count how many such tweets there are.
Hint


Question 10.
Use str_extract_all() with a regular expression to find out which Twitter users CodeClan have been tweeting.
Hint
