---
title: "Shiny Advance Homework"
output: html_notebook
---

# *Shiny - Advanced UI Homework*
# MVP
## Make an app of your choice
We have uploaded a lot of data to the data folder within the server. Have a go at reading some data in, and making a simple app from it that picks out a key insight. It can be any layout you prefer, and can be as detailed design wise as you want. The main point is to find something interesting.


```{r}
library(tidyverse)
library(shiny)
library(shinythemes)
library(CodeClanData)
library(giscoR)
library(sf)
library(leaflet)
library(leaflet.extras)
library(htmltools) 
```

```{r}
# school_census_data <- school_census #Not very interesting
whisky_data <- whisky # potential - show map
```

# Data to show:

* Map - where each distillery is in Scotland

* Distillery/Whiskys per Region

* Whiskys per Distillery

* Histogram - number of distilleries over time (with plots for number of whiskies - colour coded)

* flavours?


# Scotland Map example:
* https://stackoverflow.com/questions/67694691/drawing-map-with-ggplot-and-draw-dots-in-map

```{r}
# Scotland as a spatial object
scotland <- giscoR::gisco_get_nuts(nuts_id = 'UKM',
                                   resolution = '01') 
```

```{r}
whisky_distileries_coords <- whisky_data %>% 
  st_as_sf(coords = c("Latitude", "Longitude"), crs = 4326)
```

```{r }
mapview::mapView(whisky_distileries_coords)
```

```{r}
ggplot() +
  geom_sf(data = scotland, fill = NA, color = "gray45") + # borders of Scotland
  geom_sf(data = whisky_distileries_coords, pch = 4, color = "red") + # the distilleries
  theme_void() +
  labs(title = "Whisky of Scotland") +
  theme(plot.title = element_text(hjust = 1/2))
```

```{r}
# transfor data to spacial
whisky_data_spatial <- whisky_data %>%
  sf::st_as_sf(coords = c("Latitude", "Longitude"), crs = 4326)

# unnecessary?
# whisky_data_scotland <- sf::st_transform(whisky_data_scotland, crs = 4326)

# Create colour pallette for region
region_palette <- leaflet::colorFactor(
  palette = c(
    "Campbeltown" = "#CD3700",
    "Highlands" = "#BBFFFF",
    "Islay" = "#7CCD7C",
    "Lowlands" = "#FFDAB9",
    "Speyside" = "#912CEE"),
  domain = whisky_data_spatial$Region)

# and then plot them
whisky_map <- leaflet(whisky_data_spatial) %>% 
  addProviderTiles("Stamen.Toner") %>% 
  # addPolygons(data = scotland,
  #             fill = NA,
  #             color = "grey") %>% 
  
  addCircleMarkers(radius = 10,
                   fillOpacity = 0.7,
                   stroke = FALSE,
                   color = region_palette(
                    whisky_data_spatial$Region),
  )
                   # clusterOptions =
                   #   markerClusterOptions())
                   #    %>%
  
    # leaflet::addLegend(position = "bottomright",
    #         values = ~whisky_data_spatial,
    #         opacity = 0.7, 
    #         pal = region_palette,
    #         title = "Distillery") %>%
  
  # leaflet.extras::addResetMapButton()

whisky_map

```

