---
title: "w_10_day_1_linear_hw"
author: "Seàn M. Cusick"
date: "14/02/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r libraries}
library(tidyverse)
library(janitor)
library(GGally)
library(modelr)
library(broom)
library(ggfortify)
```

```{r data}
project_management <- clean_names(read_csv("data/project_management.csv"))
```
```{r plot}
project_management %>%
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point()
```

```{r correlation coefficient}
project_management %>%
  summarise(r = cor(estimated_length, actual_length))
```

```{r simple linear regression}
project_management_simple <- project_management %>%
  mutate(residual = estimated_length - actual_length,
         sq_residual = residual^2)
project_management_simple
```

```{r}
project_management_simple %>% 
  summarise(sum_sq_residuals = sum(sq_residual))
```
```{r linear model}
project_management_model <- lm(
  formula = estimated_length ~ actual_length,
  data = project_management_simple)

summary(project_management_model)
```
Interpret the regression coefficient of estimated_length (i.e. slope, gradient) you obtain from the model. How do you interpret the r2 value reported by the model?:

For every 4.5876 predicted days, the actual amount of days was 0.5292 more. 

```{r}
autoplot(project_management_model)
```
## Residuals vs Fitted  

Drops far away from 0 - doesn't seem reliable

## Normal Q-Q  
Normally distributed

## Scale-Location  
seems reliable

# Extension
## Residuals vs Leverage
Unsure of meaning