---
title: "w_10_d_2_diamond"
author: "Seàn M. Cusick"
date: "15/02/2022"
output:
  rmdformats::downcute:
    code_folding: hide
    downcute_theme: "chaos"
    self_contained: TRUE
    thumbnails: FALSE
    lightbox: TRUE
    gallery: FALSE
    highlight: tango
    embed_fonts: TRUE
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r libraries, include=FALSE}
library(prob)
library(tidyverse)
library(janitor)
library(ggplot2)
library(ggthemes)
library(infer)
library(e1071)
library(knitr)
library(infer)
library(viridis)
library(GGally)
library(testthat)
library(assertthat)
library(modelr)
```

# MVP {.tabset}   

## Task 1 {.tabset}  

Load the `diamonds.csv` data set and undertake an initial exploration of the data.

```{r, include=FALSE}
diamonds <- clean_names(read_csv("diamonds/data/diamonds.csv"))
```
### Variable Key 

[Via Kaggle](https://www.kaggle.com/shivam2503/diamonds/)

| Variable | Description |
|:--- |:---- |
| price | price in US dollars (\$326--\$18,823) |
| carat | weight of the diamond (0.2--5.01) |
| cut | quality of the cut (Fair, Good, Very Good, Premium, Ideal) |
| color | diamond colour, from J (worst) to D (best) |
| clarity | a measurement of how clear the diamond is (I1 (worst), SI2, SI1, VS2, VS1, VVS2, VVS1, IF (best)) |
| x | length in mm (0--10.74) |
| y | width in mm (0--58.9) |
| z | depth in mm (0--31.8) |
| depth | total depth percentage = z / mean(x, y) = 2 * z / (x + y) (43--79) |
| table | width of top of diamond relative to widest point (43--95) |

### Summary  
No `NA`s, 
```{r}
summary(diamonds)
```

***  

### Head
```{r}
head(diamonds) %>% 
  knitr::kable()
```


***  

### Distribution

```{r}
  ggpairs(diamonds) +
  scale_color_viridis(discrete = TRUE,
                      option = "D") +
  scale_fill_viridis(discrete = TRUE)
```


***  

## Task 2  
We expect the `carat` of the diamonds to be strong correlated with the physical dimensions `x`, `y` and `z`. Use `ggpairs()` to investigate correlations between these four variables.

```{r, include=FALSE}
diamond_dimension_corr <- diamonds %>%
  select(carat, x, y, z)

```

```{r}
ggpairs(diamond_dimension_corr)
```

***  

## Task 3  
Let’s drop columns `x`, `y` and `z` from the dataset, in preparation to use only carat going forward.

```{r}
diamond_minus_dimension <- diamonds %>% 
  select(-x, -y, -z)

diamond_minus_dimension
```

***  

## Task 4  
We are interested in developing a regression model for the price of a diamond in terms of the possible predictor variables in the dataset.
Use `ggpairs()` to investigate correlations between price and the predictors (this may take a while to run, don’t worry, make coffee or something).
```{r}
ggpairs(diamond_minus_dimension)
```



***  

## Task 4 - Visualisations {.tabset}  
Perform further ggplot visualisations of any significant correlations you find.

### carat v price  

```{r}
diamond_minus_dimension %>%
  ggplot(aes(x = carat, y = price)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

***  


### carat v depth  

```{r}
diamond_minus_dimension %>%
  ggplot(aes(x = carat, y = depth)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

***  

### color v price  

```{r}
diamond_minus_dimension %>%
  ggplot(aes(x = color, y = price)) +
  geom_boxplot() +
  geom_smooth(method = "lm", se = FALSE)
```



***  

### depth v table  

```{r}
diamond_minus_dimension %>%
  ggplot(aes(x = depth, y = table)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```




***  

## Task 5 {.tabset} 
Shortly we may try a regression fit using one or more of the categorical predictors `cut`, `clarity` and `color`, so let’s investigate these predictors. Investigate the levels of these predictors. How many dummy variables do you expect for each of them?

### Dummy Cut

5 Dummy variables
```{r dummy cut}
diamond_minus_dimension %>% 
  distinct(cut) %>% 
  knitr::kable()

diamond_cut_dummy <- diamond_minus_dimension %>%
  mutate(cut_ideal = ifelse(cut == "Ideal",
                            1,
                            0),
         cut_prem = ifelse(cut == "Premium",
                           1,
                           0),
         cut_good = ifelse(cut == "Good",
                           1,
                           0),
         cut_vgood = ifelse(cut == "Very Good",
                            1,
                            0),
         cut_fair = ifelse(cut == "Fair",
                           1,
                           0))

diamond_cut_dummy <- diamond_cut_dummy %>% 
  select(-cut)

diamond_cut_dummy
```

***  


### Dummy Clarity

8 dummy variables

```{r Dummy Clarity}
diamond_minus_dimension %>% 
  distinct(clarity) %>% 
  knitr::kable()

diamond_clarity_dummy <- diamond_minus_dimension %>%
  mutate(clarity_si2 = ifelse(clarity == "SI2",
                              1,
                              0),
         clarity_si1 = ifelse(clarity == "SI1",
                              1,
                              0),
         clarity_vs1 = ifelse(clarity == "VS1",
                              1,
                              0),
         clarity_vs2 = ifelse(clarity == "VS2",
                              1,
                              0),
         clarity_vvs2 = ifelse(clarity == "VVS2",
                               1,
                               0),
         clarity_vvs1 = ifelse(clarity == "VVS1",
                               1,
                               0),
        clarity_i1 = ifelse(clarity == "I1",
                            1,
                            0),
        clarity_if = ifelse(clarity == "IF",
                            1,
                            0))

diamond_clarity_dummy <- diamond_clarity_dummy %>% 
  select(-clarity)

diamond_clarity_dummy
```

***  


### Dummy Colour

7 dummy variables
```{r dummy Colour}
diamond_minus_dimension %>% 
  distinct(color) %>% 
  knitr::kable()

diamond_color_dummy <- diamond_minus_dimension %>%
  mutate(color_e = ifelse(color == "E",
                            1,
                            0),
         color_i = ifelse(color == "I",
                           1,
                           0),
         color_j = ifelse(color == "J",
                           1,
                           0),
         color_h = ifelse(color == "H",
                            1,
                            0),
         color_f = ifelse(color == "F",
                            1,
                            0),
         color_g = ifelse(color == "G",
                            1,
                            0),
         color_d = ifelse(color == "D",
                           1,
                           0))

diamond_color_dummy <- diamond_color_dummy %>% 
  select(-color)

diamond_color_dummy
```

***  

## Task 6  
Start with simple linear regression. Regress price on carat and check the regression diagnostics.


```{r line function, include=FALSE}
line <- function(x, b0, b1){
  return(b0 + x * b1)
}
```

```{r}
price_carat <- diamond_minus_dimension %>% 
  select(price, carat) %>% 
  mutate(fit_height = line(price,
                           b0 = 95,
                           b1 = 1))
```




```{r}
price_carat %>% 
  ggplot(aes(x = price,
            y = carat)) +
  geom_point() +
  geom_point(aes(y = fit_height),
             shape = 1) +
  geom_abline(slope = 1,
              intercept = 95,
              col = "red")
# +
#   geom_segment(aes(xend = price,
#                    yend = fit_height),
#                alpha = 0.5)

```

```{r}
price_carat <- price_carat %>% 
  mutate(residual = carat - fit_height,
         sq_residual = residual^2)

price_carat

price_carat %>%
  summarise(sum_sq_residuals = sum(sq_residual))
```

```{r}
price_carat_model <- lm(formula = price ~ carat, data = price_carat)
```


```{r}

price_carat <- price_carat %>% 
  select(-c(fit_height,
            residual,
            sq_residual)) %>% 
  add_predictions(price_carat_model) %>% 
  add_residuals(price_carat_model)

price_carat
  
```

```{r}
price_carat %>%
  ggplot(aes(x = price)) +
  geom_point(aes(y = carat)) +
  geom_line(aes(y = pred), col = "red")
```


***  

## Task 7  
Add another predictor of your choice. Check your assumptions, diagnostics, and interpret the model.

***  

***  

# Extension

## Task 8  
Try adding an interaction between log(carat) and your chosen categorical predictor. Do you think this interaction term is statistically justified?

***  

## Task 9  
Find and plot an appropriate visualisation to show the effect of this interaction