---
title: "ggplot_homework"
output: html_notebook
---

# Homework Info

## Learning Objectives

* Practice making plots with ggplot2
* Create your own theme and use it with plots

## Background

QikBit is a start-up company producing low cost fitness trackers. Their flagship product, the KwikBit Unit1 (spot the mistake on the patent form) reproduces the functionality of the best-in-class commercial fitness trackers, but is cheap to make. They are currently preparing to pitch to a potential investor and require a selection of charts to include in their presentation and promotional materials.

## Data

The data for this assignment is provided in the CodeClanData package.

* qb_revenue_breakdown
* qb_monthly_sales  # pivot wide 
* qb_competitors
* qb_device_data

Take a little time before you start to familiarise yourself with the data.


# MVP

## Part 1

```{r}
library(tidyverse)
library(janitor)
library(CodeClanData)
library(lubridate)
```

```{r}
revenue_breakdown <- clean_names(qb_revenue_breakdown)

monthly_sales <- clean_names(qb_monthly_sales)

competitors <- clean_names(qb_competitors)

device_data <- clean_names(qb_device_data)
```

### Question 1.
Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.

```{r}
ggplot(revenue_breakdown) +
  geom_col(aes(x = year, y = revenue, fill = product), position = "dodge")

```


### Question 2.
Make a line chart showing monthly sales of the “flagship product” - the ‘KwikBit Unit 1’ - over the last year. This data is inside qb_monthly_sales, but you will need to use filter() or subset() (base R).
```{r}
ggplot(monthly_sales) +
  geom_line(
    aes(x = date, y = amount),
    data = subset(monthly_sales, cashflow ==  "Kwikbit Unit 1 Sales"))
```


### Question 3.
Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.
```{r}
ggplot(monthly_sales) +
  aes(x = date, y = amount, colour = cashflow) +
  geom_line(
    data = subset(monthly_sales, cashflow ==  "Total Revenue")) +
  geom_line(
    data = subset(monthly_sales, cashflow ==  "Cost"))
```



### Question 4.
Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.
```{r}
competitors %>% 
  mutate(revenue_thousands = revenue/1000) %>% 

ggplot() +
  geom_area(
    aes(x = year, y = revenue_thousands, group = company, fill = company)) +
  ylab ("revenue (1000s)")
```



### Question 5.
Now show the sales from the four competitors as a line graph. Include an extra layer that shows the data points used to make the lines.
```{r}
ggplot(competitors) + 
  aes(x = year, y = revenue, colour = company) +
  geom_line(aes(group = company), alpha = 1) +
  geom_point(alpha = 0.5) 
```



### Question 6.
Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between companies and people. The data for this is in qb_device_data.

```{r}
device_data %>% 
  mutate(time_text = str_c(hours, mins), time_date = hm(time_text)) %>%  

ggplot(device_data) + 
  aes(x = time_date, y = count, group = id, colour = device) +
  geom_line()
```




## Part 2

Take the plots that you produced in part one and now polish them by:

Adding appropriate labels
Changing the scales and coordinates when appropriate.
Applying a unified theme, which is described below:
Graphs should have white backgrounds, and use colour sparingly.
There should be faint grid lines.
Font sizes should be ~12pt although titles should be slightly larger and axis labels can be slightly smaller.
All plots should use colours from the following company colour scheme.

```{r}
col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")
```



# Extension

Try out different ways of plotting these three datasets. Which graphs do you think are particularly effective at showing QikBit’s success?