---
title: "week06_day1, probability homework"
output: html_notebook
---

```{r}
library(prob)
library(gtools)
library(tidyverse)
library(janitor)
```


# MVP

## The Titanic 

A data set detailing the survival or death of passengers and crew members on the RMS Titanic is given in the data folder for this homework - use this data and not the built-in Titanic dataset in R.

Some time after the disaster a journalist wrote that crew members were more likely to have survived the sinking than passengers. This was disputed by a descendant of one of the surviving crew members, who suggested that the opposite was true, i.e. passengers were more likely to have survived than crew.

### Question

Calculate the conditional probabilities prob(survived∣crew) and prob(survived∣passenger) to settle this dispute.

Have a look at the distinct values of the class variable, this will tell you whether each individual was a passenger (1st, 2nd or 3rd class) or a member of the crew (treat restaurant staff as crew)

### Hints
* You may want to create a crew column containing values TRUE or FALSE to help with this
* For prob(survived∣crew) think ‘what proportion of the crew survived?’, and similar for prob(survived∣passenger)

```{r}
titanic_data <- read.csv("data/titanic.csv")

titanic_data <- titanic_data %>%
  mutate(
    crew = case_when(
      str_detect(class, "crew") ~ TRUE,
      str_detect(class, "staff") ~ TRUE,
      TRUE ~ FALSE),
    .after = age) %>% 
  mutate(
    survived = case_when(
      str_detect(survived, "yes") ~ TRUE,
      str_detect(survived, "no") ~ FALSE,
      TRUE ~ FALSE)
  )

  

# prob_survived_crew <- titanic_data %>% 
#   filter
# 
# 
# prob_survived_passenger
```

```{r}
titanic_table <- titanic_data %>% 
  tabyl(crew, survived)

titanic_table
```
```{r}
titanic_table <- titanic_table %>% 
  adorn_totals(where = c("row", "col"))


titanic_table
```
```{r}
prob_crew <- titanic_data %>% 
  summarise(prob = sum(crew == TRUE) / n())

prob_crew
```

```{r}
prob_passenger <- titanic_data %>% 
  summarise(prob = sum(crew == FALSE) / n())

prob_passenger
```


```{r}
# prob_survived_crew <- titanic_data %>% 
#   filter(survived == TRUE, crew == TRUE) %>% summarise(prob = n() / nrow(titanic_data))
   
prob_survived_crew <- titanic_data %>% 
  filter(survived == TRUE, crew == TRUE) %>% summarise(prob = n() / nrow(titanic_data))

prob_survived_crew
```

```{r}
prob_survived_passenger <- titanic_data %>% 
  filter(survived == TRUE, crew == FALSE) %>% summarise(prob = n() / nrow(titanic_data))

prob_survived_passenger
```


## Probability Consolidation Questions

### Question 1.
If I roll a six-sided dice once, what is the probability of getting a number less than 5?

A: 0.6666667

```{r}
one_die <- rolldie(1)

less_than_five <- one_die %>% 
  dplyr::filter(X1 < 5)

prob_less_than_five <- nrow(less_than_five) / nrow(one_die)
prob_less_than_five
```

### Question 2.
How many outcomes are there in the sample space of an experiment in which we toss three dice?

A: 216
```{r}
three_dice <- rolldie(3)

nrow(three_dice)
```


### Question 3.
In an experiment where we roll four dice:

* how many outcomes are in the event where the total of the four dice equals 5, 6 or 7)?
A: 9

* what is the probability of this event?
A: 0.006944444

* what assumptions do we apply in answering part ii?
A: the same set of dice are used and rolled in the same manner

```{r}
four_dice <- rolldie(4) %>% 
  mutate(total = rowSums(.),
         .after = X4)


total_5_to_7 <- four_dice %>% 
  dplyr::filter(total %in% c(5, 6, 7))

nrow(total_5_to_7)

prob_total_5_to_7 <- nrow(total_5_to_7) / nrow(four_dice)
prob_total_5_to_7
```


#### Hint
For part i, rowSums(.) may help you setup up the necessary random variable total (or you can use pivot_longer())


### Question 4.
Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?

A:

```{r}

```


#### Hint
This is an arrangement where order matters. Of all the possible arrangements, how many are correct?


### Question 5.
I roll six dice:

* what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?
A:

* what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?
A:

```{r}

```


#### Hint
Have a look at the isin() function in the prob package. For example, to filter all rows containing 6, 1, 2 in that order, you could use isin(., c(6, 1, 2), ordered = TRUE)



### Question 6.
If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades?

A:

#### Hint
* Investigate the cards() function in the prob package, if you’d like to try this in R (make a deck without jokers).
* You could think about adding your own black_card random variable to the sample space, which would be TRUE if the suit is ‘Spade’ or ‘Club’, and FALSE otherwise.)

```{r}
card_deck_52 <- cards(jokers = FALSE) %>% 
  mutate(row = row_number(),
         .before = rank)



card_deck_52 <- card_deck_52 %>% 
  mutate(
    blac_suit = (suit == "Club" | suit =="Spade"))

card_deck_52
```


